Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/contributions.tex
Updated the contributions ot be letter paper, not A4 paper

\documentclass[a4paper,12pt]{article}

@@

%----------- Choose Margins ----------%
\usepackage[a4paper,margin=1.87cm]{geometry}

@@

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team (QSAT), 2017 -- 2018}. 
    I took on a mentorship role at QSAT, where I taught C++, Git, and information
    theory to the team's software developers. I helped them organize
    the satellite codebase, managed all code reviews, and provided advice for my
    peers rather than writing software myself.

>>>>

\documentclass[letterpaper,12pt]{article}

@@

%----------- Choose Margins ----------%
\usepackage[letterpaper,margin=1.87cm]{geometry}

@@

%\item \textbf{Science Payload Designer, Queen’s University Satellite Design
%    Team (QSAT), 2017 -- 2018}. 
%    I took on a mentorship role at QSAT, where I taught C++, Git, and information
%    theory to the team's software developers. I helped them organize
%    the satellite codebase, managed all code reviews, and provided advice for my
%    peers rather than writing software myself.
